
\documentclass[11pt]{moderncv}

\moderncvstyle{csardi}
\moderncvcolor{wes}

\bibliography{pubs}

\name{gábor}{csárdi}
\title{computer scientist}

\input{vc}

\begin{document}

\RaggedRight

\makecvtitle

\begin{aside}
\section{about}
\faEnvelope\ 334 Harvard st L3,\\
\textcolor{color4}{\faEnvelope}\ 02139 Cambridge, MA\\
\faPhone\ +1 (857) 259-0417\\
@\ \nolinebreak{}csardi.gabor@gmail.com\\
\faGlobe\ gaborcsardi.org\\
\faTwitter\ @gaborcsardi\\
\faGithub\ gaborcsardi
\section{skills}
Algorithms and data structures.
Graph algorithms, network analysis.
Statistical model building, inference,
machine learning, Bayesian statistics.\\[6pt]
Expert: R, C, Linux/Unix, Shell.\\
Experienced: C++, Python, JavaScript,
  Java, HTML/CSS, \LaTeX.\\[6pt]
SQL and noSQL databases.\\[6pt]
Software engineering tools,
git, Jenkins CI, etc.
% Hadoop
% Apache spark

\section{languages}
Fluent: English, Hungarian\\
Basic: German
\end{aside}

\section{interests}

Network science, graph algorithms, analysis of network data.
Data science, data mining, machine learning.
Bioinformatics and computational biology. RNA-Seq analysis,
alternative splicing.

\section{education}

\cventry{2003--2008}{PhD}{Eötvös University}{Budapest, Hungary}%
{Computer Science}%
{Dissertation: Modeling complex systems as evolving networks\\
Summa cum laude.}

\cventry{1998--2003}{MSc}{Eötvös University}{Budapest, Hungary}%
{Computer Science}%
{Graduated with distinction (single in class).\\
Specialized in Programming Languages, Databases, Machine Learning and
Economics.}

\section{experience}

\cventry{2011--2015}{Postdoctoral researcher}{Department of Statistics,
Harvard University}{Cambridge, MA, USA}{}{}

\cventry{2008--2011}{Postdoctoral researcher}{Computational Biology Group,
Department of Medical Genetics, University of Lausanne}{Lausanne, Switzerland}%
{}{}

\cventry{2006--2007}{Research Fellow}{Department of Biophysics, Research
Institute for Particle and Nuclear and Physics, Hungarian
Academy of Sciences.}{Budapest, Hungary}%
{}{}

\cventry{2003--2006}{Research Assistant}{Department of Biophysics, Research
Institute for Particle and Nuclear and Physics, Hungarian
Academy of Sciences.}{Budapest, Hungary}%
{}{}

\cventry{2002, 2004, 2005, 2006}{Research and teaching assistant}{Three months
each, Center for Complex Systems Studies, Kalamazoo College, Kalamazoo, MI,
USA.}{Kalamazoo, MI, USA}%
{}{}

\cventry{2002}{Erasmus student}{Department of Biomedical
Engineering, Eindhoven University of Technology}{Eindhoven, The Netherlands.}%
{}{}

\section{applications}
\cventry{2005--}{igraph}{Library for network analysis and graph algorithms}%
{C/C++/R/Python}{\url{http://igraph.org}}{}

\cventry{2014--}{metacran}{Tools for the CRAN R package repository}%
{R/JavaScript}{\url{https://github.com/metacran/metacran}}{}

\cventry{2011--}{MISO}{Mixture of isoforms model for RNA-Seq
 isoform quantitation}%
{Python/C}{\url{http://genes.mit.edu/burgelab/miso/index.html}}{}

\cventry{2011--}{Other software}{See \url{http://github.com/gaborcsardi}}%
{}{}{}

\pagebreak

\section{publications}

\begin{refsection}
  \nocite{*}
  \printbibliography[type={book}, title={books}, heading=subbibliography]
\end{refsection}

\begin{refsection}
  \nocite{*}
  \printbibliography[type={article}, title={articles}, heading=subbibliography]
\end{refsection}

\begin{refsection}
  \nocite{*}
  \printbibliography[nottype={book}, nottype={article},
  title={other}, heading=subbibliography]
\end{refsection}

\section{awards}

\cventry{2012}{\mdseries Best 5 minute postdoc presentation at the Harvard Symposium of
Applied Statistics}{}{}{}{}

\cventry{2008}{\mdseries Scholarship to the FEBS course on ``Structural variations in genome,
gene expression, Single cell analysis: Arrays, Beads, High-throughput
sequencing''}{}{}{}{}

\cventry{2006}{\mdseries Student grant to the International Conference on Artificial Neural
Networks}{}{}{}{}

\cventry{2004}{\mdseries Scholarship to the Santa Fé Complex Systems Summer School}{}{}{}{}

\cventry{2003--2006}{\mdseries Young researcher scholarship of the Hungarian Academy
of Sciences}{}{}{}{}

\cventry{2003}{\mdseries Graduated in computer science with distinction, Eötvös University,
Faculty of Science}{}{}{}{}

\cventry{2002}{\mdseries Distinguished student of the faculty award, Eötvös
University, Faculty of Science}{}{}{}{}

\cventry{2002}{\mdseries Erasmus scholarship, Eindhoven University of Technology,
five months}{}{}{}{}

\section{service}

Associate Editor of Journal of Statistical Software.

Reviewing for Journal of Statistical Software, Journal of Machine
Learning Research, Physical Review E, Bioinformatics, Physica A,
Biosystems, Computational Statistics and Data Analysis,
Neural Information Processing Systems, International Conference
on Artificial Intelligence and Statistics.

\end{document}
